### 2017-12-06 submission/manuscript.Rmd
add PCR protocol to methods

@@

***PCR Protocol:***
The five different high fidelity Taq DNA polymerase that were tested were AccuPrime^TM^ (ThermoFisher, MA, USA), KAPA HIFI (Roche, IN, USA).

>>>>

#Read in the meta data file
metadata <- read_csv("../data/process/tables/meta_data.csv")

@@

***PCR Protocol:***
The five different high fidelity (HiFi) Taq DNA polymerase that were tested were AccuPrime^TM^ (ThermoFisher, MA, USA), KAPA HIFI (Roche, IN, USA), Phusion (ThermoFisher, MA, USA), Platinum (ThermoFisher, MA, USA), and Q5 (New England Biolabs, MA, USA). The PCR cycle conditions were the same for every primer [@protocol_Kozich_2013] (https://github.com/SchlossLab/MiSeq_WetLab_SOP/blob/master/MiSeq_WetLab_SOP_v4.md). If the HiFi Taq had a specific activation time that was different then 2 minutes that was used instead. The 30 cycle default was used but the cycle conditions started at 15 and increased by 5 up to 35 cycles and was used for both fecal and mock samples. The fecal PCR consisted of all 4 samples at 15, 20, 25, 30, and 35 cycles for each Taq (total samples = 100). Although, the mock communities also had 4 replicates used for 15, 20, 25, and 35 cycles, 10 replicates were used for 30 cycles for all Taq (total samples = 130). For all the mock community samples there was not enough PCR product at 15 cycles for adequate sequencing.

### 2017-12-06 submission/manuscript.tex
add PCR protocol to methods

\textbf{\emph{PCR Protocol:}} The five different high fidelity Taq DNA
polymerase that were tested were AccuPrime\textsuperscript{TM}
(ThermoFisher, MA, USA), KAPA HIFI (Roche, IN, USA).

@@

\hypertarget{refs}{}
\hypertarget{ref-erin_seekatz_2016}{}
Seekatz AM., Rao K., Santhosh K., Young VB. 2016. Dynamics of the fecal
microbiome in patients with recurrent and nonrecurrent clostridium
difficile infection. \emph{Genome Medicine} 8. DOI:
\href{https://doi.org/10.1186/s13073-016-0298-8}{10.1186/s13073-016-0298-8}.

>>>>

\textbf{\emph{PCR Protocol:}} The five different high fidelity (HiFi)
Taq DNA polymerase that were tested were AccuPrime\textsuperscript{TM}
(ThermoFisher, MA, USA), KAPA HIFI (Roche, IN, USA), Phusion
(ThermoFisher, MA, USA), Platinum (ThermoFisher, MA, USA), and Q5 (New
England Biolabs, MA, USA). The PCR cycle conditions were the same for
every primer (Kozich et al., 2013)
(\url{https://github.com/SchlossLab/MiSeq_WetLab_SOP/blob/master/MiSeq_WetLab_SOP_v4.md}).
If the HiFi Taq had a specific activation time that was different then 2
minutes that was used instead. The 30 cycle default was used but the
cycle conditions started at 15 and increased by 5 up to 35 cycles and
was used for both fecal and mock samples. The fecal PCR consisted of all
4 samples at 15, 20, 25, 30, and 35 cycles for each Taq (total samples =
100). Although, the mock communities also had 4 replicates used for 15,
20, 25, and 35 cycles, 10 replicates were used for 30 cycles for all Taq
(total samples = 130). For all the mock community samples there was not
enough PCR product at 15 cycles for adequate sequencing.

@@

\hypertarget{refs}{}
\hypertarget{ref-protocol_Kozich_2013}{}
Kozich JJ., Westcott SL., Baxter NT., Highlander SK., Schloss PD. 2013.
Development of a dual-index sequencing strategy and curation pipeline
for analyzing amplicon sequence data on the MiSeq illumina sequencing
platform. \emph{Applied and Environmental Microbiology} 79:5112--5120.
DOI: \href{https://doi.org/10.1128/aem.01043-13}{10.1128/aem.01043-13}.

\hypertarget{ref-erin_seekatz_2016}{}
Seekatz AM., Rao K., Santhosh K., Young VB. 2016. Dynamics of the fecal
microbiome in patients with recurrent and nonrecurrent clostridium
difficile infection. \emph{Genome Medicine} 8. DOI:
\href{https://doi.org/10.1186/s13073-016-0298-8}{10.1186/s13073-016-0298-8}.
